Comparing corrosion control treatments using a robust Bayesian generalized additive model

### 2022-05-09 README.Rmd
added DOI

This repository contains the R code and other materials for the paper "Comparing corrosion control treatments using a robust Bayesian generalized additive model".

>>>>

This repository contains the R code and other materials for the paper "Comparing corrosion control treatments using a robust Bayesian generalized additive model", currently available as a [preprint](http://doi.org/10.26434/chemrxiv-2022-b3f72). Bespoke functions used to fit the models are available as a separate package, [`bgamcar1`](https://github.com/bentrueman/bgamcar1).

### 2022-05-09 Rmarkdown/paper-si.Rmd
added DOI

---
title: "Supplementary information for *Comparing corrosion control treatments using a robust Bayesian generalized additive model*"
author: "Benjamin F. Trueman^§^, Wendell James^†^, Trevor Shu^†^, Evelyne Dor&eacute;^§^, and Graham A. Gagnon^§^"
date: "^§^Centre for Water Resources Studies, Department of Civil & Resource Engineering, Dalhousie University, 1360 Barrington St., Halifax, NS, CAN B3H 4R2    \n&nbsp;    \n&nbsp;^†^EPCOR Water Services, Edmonton, AB, CAN"
output:
  word_document:
    keep_md: no
    reference_docx: StylesTemplate.docx
  html_document: default
bibliography: references.bib
csl: environmental-science-and-technology.csl
---

>>>>

---
title: "Supplementary information for *Comparing corrosion control treatments using a robust Bayesian generalized additive model*"
author: "Benjamin F. Trueman^§,\\*^, Wendell James^†^, Trevor Shu^†^, Evelyne Dor&eacute;^§^, and Graham A. Gagnon^§^"
date: "^§^Centre for Water Resources Studies, Department of Civil & Resource Engineering, Dalhousie University, 1360 Barrington St., Halifax, NS, CAN B3H 4R2    \n&nbsp;    \n&nbsp;^†^EPCOR Water Services, Edmonton, AB, CAN    \n&nbsp;    \n&nbsp;^\\*^Corresponding author: benjamin.trueman@dal.ca"
output:
  word_document:
    keep_md: no
    reference_docx: StylesTemplate.docx
  html_document: default
bibliography: references.bib
csl: environmental-science-and-technology.csl
---

### 2022-05-09 Rmarkdown/paper.Rmd
added DOI

---
title: "Comparing corrosion control treatments using a robust Bayesian generalized additive model"
author: "Benjamin F. Trueman^§^, Wendell James^†^, Trevor Shu^†^, Evelyne Dor&eacute;^§^, and Graham A. Gagnon^§^"
date: "^§^Centre for Water Resources Studies, Department of Civil & Resource Engineering, Dalhousie University, 1360 Barrington St., Halifax, NS, CAN B3H 4R2    \n&nbsp;    \n&nbsp;^†^EPCOR Water Services, Edmonton, AB, CAN"
output:
  word_document:
    keep_md: no
    reference_docx: StylesTemplate.docx
  html_document: default
bibliography: references.bib
csl: environmental-science-and-technology.csl
---

>>>>

---
title: "Comparing corrosion control treatments using a robust Bayesian generalized additive model"
author: "Benjamin F. Trueman^§,\\*^, Wendell James^†^, Trevor Shu^†^, Evelyne Dor&eacute;^§^, and Graham A. Gagnon^§^"
date: "^§^Centre for Water Resources Studies, Department of Civil & Resource Engineering, Dalhousie University, 1360 Barrington St., Halifax, NS, CAN B3H 4R2    \n&nbsp;    \n&nbsp;^†^EPCOR Water Services, Edmonton, AB, CAN    \n&nbsp;    \n&nbsp;^\\*^Corresponding author: benjamin.trueman@dal.ca"
output:
  word_document:
    keep_md: no
    reference_docx: StylesTemplate.docx
  html_document: default
bibliography: references.bib
csl: environmental-science-and-technology.csl
---
